---
title: "HW3"
output: github_document
---

```{r, message = FALSE}
library(tidyverse)
library(p8105.datasets)
library(patchwork)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

```{r}
data("instacart") 
instacart

instacart %>% 
  group_by(order_id) %>% 
  summarize(n_obs = n()) 

instacart %>% 
  count(aisle_id)
```

The `instacart` dataset has `r ncol(instacart)` variables and `r nrow(instacart)` observations. Each observation is an item added to an Instacart order. The dataset describes those orders in terms of which items had been previously ordered by ths customer (`reordered`), what order they were added to the cart (`add_to_cart_order`), and additional product details (`product id`, `product_name`, `aisle`, and `department`). For example, we know that for the first order (`order_id` = 1), customer `r pull(filter(instacart, order_id == 1, add_to_cart_order ==1), user_id)` placed their `r pull(filter(instacart, order_id == 1, add_to_cart_order ==1), order_number)`th order `r pull(filter(instacart, order_id == 1, add_to_cart_order ==1), days_since_prior_order)` days after their prior order. they ordered `r max(pull(filter(instacart, order_id == 1), add_to_cart_order))` items. 

```{r}
instacart %>% 
  group_by(aisle_id) %>% 
  summarize (n_obs = n()) %>% 
  arrange(desc(n_obs))
  
```

There are 134 aisles in this dataset and aisles 83 (`r pull(distinct(filter(instacart, aisle_id == 83), aisle))`) and 24 (`r pull(distinct(filter(instacart, aisle_id == 24), aisle))`) have the most items ordered from them with over 150,000 items per aisle. 

```{r}
instacart %>% 
  group_by(aisle_id) %>% 
  summarize (n_obs = n()) %>% 
  filter(n_obs > 10000) %>% 
  mutate(aisle_id = fct_reorder(as.factor(aisle_id), n_obs)) %>% 
  arrange(desc(n_obs)) %>% 
  ggplot(aes(x = aisle_id, y = n_obs)) +
  geom_point() + 
  labs(
    title = "Items (over 10,000) ordered per aisle", 
    x = "Aisle Number", 
    y = "Number of Items Ordered", 
    caption = "Data from p8105 package `Instacart`"
  ) 
```

## HOW TO FIX SCALE

```{r, message = FALSE}
instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  select(aisle, product_name) %>% 
  group_by(aisle, product_name) %>% 
  summarize(number_ordered = n()) %>% 
  filter(number_ordered == max(number_ordered)) %>% 
  arrange(desc(number_ordered)) %>% 
  knitr::kable(caption = "Most popular products in selected aisles")
```

```{r, message = FALSE}
instacart %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  select(product_name, order_dow, order_hour_of_day) %>% 
  group_by(product_name, order_dow) %>% 
  summarize(mean_hour = mean(order_hour_of_day)) %>% 
  pivot_wider(names_from = order_dow, values_from = mean_hour) %>% 
  rename("Sunday" = "0", "Monday" = "1", "Tuesday" = "2", "Wednesday" = "3", "Thursday" = "4", "Friday" = "5", "Saturday" = "6") %>% 
  knitr::kable(caption = "Mean hour of the day select items are ordered")
```


## Problem 2

```{r}
data("brfss_smart2010") 
brfss_smart2010

brfss = brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health") %>% 
  mutate(response = as.factor(response), response = factor(response, levels = c("Poor", "Fair", "Good", "Very good", "Excellent")))
  
```

```{r}
brfss %>% 
  filter(year == 2002) %>% 
  group_by(locationabbr, locationdesc) %>% 
  summarise(n_obs = n()) %>% 
  count(locationabbr) %>% 
  filter(n >= 7) %>% 
  arrange(n)
```

In 2002, Connecticut, Florida, and North Carolina were each observed at 7 locations, Massachusetts and New Jersey were observed at 8 locations, and Pennsylvania was observed at 10 locations. 

```{r}
brfss %>% 
  filter(year == 2010) %>% 
  group_by(locationabbr, locationdesc) %>% 
  summarise(n_obs = n()) %>% 
  count(locationabbr) %>% 
  filter(n >= 7) %>% 
  arrange(n)
```

In 2010, the following states were observed at the following number of locations: 
* 7 locations: Colorado, Pennsylvania, and South Carolina 
* 8 locations: Ohio 
* 9 locations: Massachusetts and New York 
* 10 locations: Nebraska and Washington 
* 12 locations: California, Maryland, and North Carolina 
* 16 locations: Texas 
* 19 locations: New Jersey 
* 41 locations: Florida 

```{r}
spaghetti = brfss %>% 
  filter(response == "Excellent") %>% 
  group_by(year, locationabbr) %>% 
  summarize(avgvalue = mean(data_value))

spaghetti %>% 
  ggplot(aes(x = year, y = avgvalue, group = locationabbr, color = locationabbr)) + 
  geom_line() 
  
nys2006 = brfss %>% 
  filter(year == 2006, locationabbr == "NY") %>% 
  group_by(locationdesc, response) 

nys2010 = brfss %>% 
  filter(year == 2010, locationabbr == "NY") %>% 
  group_by(locationdesc, response) 

nys2006_plot = nys2006 %>% 
  ggplot(aes(x = response, y = data_value, group = locationdesc, color = locationdesc)) + 
  geom_line()

nys2010_plot = nys2010 %>% 
  ggplot(aes(x = response, y = data_value, group = locationdesc, color = locationdesc)) + 
  geom_line()

(nys2006_plot + nys2010_plot)
  
```






